---
title: "Milestone 3"
author: "Miroslav Bergam"
date: "10/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warnings = FALSE)

#Importing tools like read_csv(), filter(), and count() from tidyverse package

library(tidyverse)

```

```{r reading data}
spotify_data <- read.csv("music-data/regional-us-weekly-2019-09-06--2019-09-13.csv")
billboard_data <- read.csv("music-data/Hot Stuff.csv")
```


I retrieved the Spotify CSV data directly from Spotify's website, which
conveniently allows one to download CSV files of its weekly, monthly, and yearly
chart data. The file I added to this repository is data from a singular week,
but I can also retrieve a wider range of data from the website through the same
means. Billboard does not make it's data as easily accessible, therefore I
retrieved this CSV file from a data.world user that compiled weekly chart data
from 1958 to June 2019.

Thus far, I have stored the files in a directory labelled music-data and stored
them into variables entitled spotify-data and billboard-data. I will use these
files, or files from these sources, to make a visual on song positions,
comparing how Spotify/streaming positions differ compared to their Billboard
positions, which also factors in Youtube, iTunes, and physical sales. I can also
use this data to visualize the number of unique #1 hits in each year, analyzing
the longevity of music hits and looking for trends across platforms and years. I
can also look at songs' durations on the charts with this data, and how that
differs by platform. However, I may create a graphic that analyzes song sales by
numbers and how streaming (specifically Spotify) has come to dominate the bulk
of song data (over digital and physical copies). Because the two files in this
repo lack the sales in numbers, I would have to also scrape data from kworb.net,
RIAA, and/or Nielson, if I choose to take my project in this direction.